\emph{Light Exposure Behavior Assessment (LEBA)}: Development of a novel instrument to capture light exposure-related behaviours

### 2022-01-07 appendix-2.Rmd
Aesthetic Updates

```{r MinRes, include=F}
library(psych)
library(tabledown)
library(kableExtra)#without this pdf rendering will not happen

data <- readRDS("leba_2021-09-08.rds")

@@

#Separating the EFA and CFA(only items)
sem.data <- data[, 9:56] #EFA & CFA data
sem.data[ sem.data == 0] <- 1 #Merged "0"s and "1"s into "1"s

## renaming the column-header
prefix <- "item"
sufix <- c(1:48)
colnam <- paste(prefix,sufix, sep = "" )
colnames(sem.data) <- colnam

### EFA data
EFA.data <- sem.data[1:428, ]
#Polychoric Correlation matrix

correlations <- psych::polychoric(EFA.data, correct = 0)

#Supplementary EFA with Minres Extraction

fa.5F.min.1 <- fa(r=correlations$rho, nfactors = 5, fm= "minres",rotate ="varimax",
                residuals = TRUE, SMC = TRUE, n.obs =428)
EE <- print(fa.5F.min.1, cut = .3, digits = 3, sort = TRUE)

reduced.model.5F.min.1 <- dplyr::select(EFA.data ,
                                    -c( item20, item19, item5, item31, item44, item24, item43, item39, item22, item2, item18, item48, item42, item29, item6, item15, item23, item28, item14))

correlations.red.5F.min.1 <- polychoric(reduced.model.5F.min.1,correct = 0)

fa.5F.min.2 <- fa(r=correlations.red.5F.min.1$rho, nfactors = 5, fm= "minres",rotate ="varimax",
              residuals = TRUE, SMC = TRUE, n.obs =428)

FF <- print(fa.5F.min.2, cut = .3, digits = 3, sort = TRUE)

reduced.model.5F.min.2 <- dplyr::select(EFA.data, -c( item20, item19, item5, item31, item44, item24, item43, item39, item22, item2, item18, item48, item42, item29, item6, item15, item23, item28, item14, item34, item47, item21, item13))

correlations.red.5F.min.2 <- polychoric(reduced.model.5F.min.2, correct = 0)

fa.5F.min.3 <- fa(r=correlations.red.5F.min.2$rho, nfactors = 5, fm= "minres",rotate ="varimax",
              residuals = TRUE, SMC = TRUE, n.obs =428)

GG <- print(fa.5F.min.3, cut = .3, digits = 3, sort = TRUE)

minresTab <- tabledown::fac.tab(fa.5F.min.3, cut =.3,complexity = F)
```

```{r MinResTab}
papaja::apa_table(minresTab,  caption = "Factor loadings and communality of the retained items (Minmum Residual)", note = "Only loading higher than .30 is reported", longtable=T, font_size = "small")
```

# Factor analysis with six factors

```{r sixFac, include=F}
# EFA with 6 factor (rejected)

#correlations <- polychoric(EFA.factor, correct = 0)

fa.6F.1 <- fa(r=correlations$rho, nfactors = 6, fm= "pa",rotate ="varimax",
              residuals = TRUE, SMC = TRUE, n.obs =428)

II <- print(fa.6F.1, cut = .3, digits = 3, sort = TRUE)

reduced.model.6F.1 <- dplyr::select(EFA.data ,
                                    -c(item34, item44, item48, item43, item39, item22, item2, item20, item21, item24,item30, item14, item28, item6, item15, item23))

correlations.red.6F.1 <- polychoric(reduced.model.6F.1,correct = 0)

fa.6F.2 <- fa(r=correlations.red.6F.1$rho, nfactors = 6, fm= "pa",rotate ="varimax",
              residuals = TRUE, SMC = TRUE, n.obs =428)

JJ <- print(fa.6F.2, cut = .3, digits = 3, sort = TRUE)

reduced.model.6F.2 <- dplyr::select(EFA.data, -c(item34, item44, item48, item43, item39, item22, item2, item20, item21, item24,item30, item14, item28, item6, item15, item23, item18, item42, item47, item41))

correlations.red.6F.2 <- polychoric(reduced.model.6F.2,correct = 0)

fa.6F.3 <- fa(r=correlations.red.6F.2$rho, nfactors = 6, fm= "pa",rotate ="varimax",
              residuals = TRUE, SMC = TRUE, n.obs =428, max.iter = 500)

KK <- print(fa.6F.3, cut = .3, digits = 3, sort = TRUE)

reduced.model.6F.3 <- dplyr::select(EFA.data, -c(item34, item44, item48, item43, item39, item22, item2, item20, item21, item24,item30, item14, item28, item6, item15, item23, item18, item42, item47, item41, item5, item13, item29))

correlations.red.6F.3 <- polychoric(reduced.model.6F.3,correct = 0)

fa.6F.4 <- fa(r=correlations.red.6F.3$rho, nfactors = 6, fm= "pa",rotate ="varimax",
              residuals = TRUE, SMC = TRUE, n.obs =428, max.iter = 500)

ll <- print(fa.6F.4, cut = .3, digits = 3, sort = TRUE)

reduced.model.6F.4 <- dplyr::select(EFA.data, -c(item34, item44, item48, item43, item39, item22, item2, item20, item21, item24,item30, item14, item28, item6, item15, item23, item18, item42, item47, item41, item5, item13, item29, item19))

correlations.red.6F.4 <- polychoric(reduced.model.6F.4,correct = 0)

fa.6F.5 <- fa(r=correlations.red.6F.4$rho, nfactors = 6, fm= "pa",rotate ="varimax",
              residuals = TRUE, SMC = TRUE, n.obs =428, max.iter = 500)

mm <- print(fa.6F.5, cut = .3, digits = 3, sort = TRUE)

# Residuals
residual.6F =residuals(fa.6F.5 , diag = FALSE, na.rm =T)
#Count of numbers of residuals>.05
BigRRR= sum(residual.6F>abs(.05), na.rm =T)
print(BigRRR)

#Total number of off diagonal elements in the data matrix
totRRR = length(reduced.model.6F.2)*(length(reduced.model.6F.2)-1)/2

# Proportion of off-diagonal elements >.10
sumRRR <- sum(BigRRR/totRRR*100)

#hist(residual.6F, main = NULL, xlab = "Six factor Solution: Residuals",ylim=c(0, 400))
#abline(h =65, lwd = 2, lty = 2)
#abline(v =.05,lwd = 2, lty = 2)
sixFac <- tabledown::fac.tab(fa.6F.5, cut =.3,complexity = F)
```

```{r sixFacTab, results='asis'}
papaja::apa_table(sixFac,  caption = "Factor loadings and communality of the retained items(six factor)", note = "Only loading higher than .30 is reported; Sixth factor has only two salient loadings",longtable =T, font_size = "small")
```

```{r DataAppB, include=FALSE}
data <- readRDS("leba_2021-09-08.rds")

#Separating the EFA and CFA(only items)
sem.data <- data[, 9:56] #EFA & CFA data
## renaming the column-header
prefix <- "item"
sufix <- c(1:48)
colnam <- paste(prefix,sufix, sep = "" )
colnames(sem.data) <- colnam
EFA.data <- sem.data[1:428, ]

```

```{r ggplot2AppB, include=F}
apatheme=ggplot2::theme_bw()+
  ggplot2::theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        #text=element_text(family = "Helvetica",),
        legend.title=element_blank(),
        axis.line.x = element_line(color='black'),
        axis.line.y = element_line(color='black'),
        panel.border = element_rect(color = "black",
                                    fill = NA,
                                    size = 1))
```

```{r EFAAppB, include=FALSE}
fa.5F.1 <- fa(r=correlations$rho, nfactors = 5, fm= "pa",rotate ="varimax",
              residuals = TRUE, SMC = TRUE, n.obs =428)
AA <- print(fa.5F.1, cut = .3, digits = 3, sort = TRUE)

reduced.model.5F.1 <- dplyr::select(EFA.data ,
                                    -c(item32, item34, item24, item37, item22, item5,
                                        item28, item30, item39,item23, item45, item6, item29, item2, item41))

correlations.red.5F.1 <- polychoric(reduced.model.5F.1,correct = 0)

fa.5F.2 <- fa(r=correlations.red.5F.1$rho, nfactors = 5, fm= "pa",rotate ="varimax",
              residuals = TRUE, SMC = TRUE, n.obs =428)

BB <- print(fa.5F.2, cut = .3, digits = 3, sort = TRUE)

reduced.model.5F.2 <- dplyr::select(EFA.data, -c( item32, item34, item24, item37, item22, item5,
                                        item28, item30, item39,item23, item45, item6, item29, item2, item41, item46, item13, item15, item25, item1, item26, item14))

correlations.red.5F.2 <- polychoric(reduced.model.5F.2,correct = 0)

fa.5F.3 <- fa(r=correlations.red.5F.2$rho, nfactors = 5, fm= "pa",rotate ="varimax",
              residuals = TRUE, SMC = TRUE, n.obs =428,max.iter = 500 )

CC <- print(fa.5F.3, cut = .3, digits = 3, sort = TRUE)

reduced.model.5F.3 <- dplyr::select(EFA.data, -c( item32, item34, item24, item37, item22, item5,
                                        item28, item30, item39,item23, item45, item6, item29, item2, item41, item46, item13, item15, item25, item1, item26, item14, item43, item42))

correlations.red.5F.3 <- polychoric(reduced.model.5F.3,correct = 0)

fa.5F.4 <- fa(r=correlations.red.5F.3$rho, nfactors = 5, fm= "pa",rotate ="varimax",
              residuals = TRUE, SMC = TRUE, n.obs =428,max.iter = 500 )

CC <- print(fa.5F.4, cut = .3, digits = 3, sort = TRUE)
```

```{r factordetailsAppB, include=FALSE}
#Preparing the EFA table
efa.table <- tabledown::fac.tab(fa.5F.4,.3, complexity = F) 
```

```{r efaunmerged, results='asis'}
apa_table(efa.table, caption = "Factor loadings and communality of the retained items in five factor solution [Unmerged Responses]", note = "Only loading higher than .30 is reported", longtable =T, font_size = "small")
```

```{r EFAAppsix, include=FALSE, warning=F,message=FALSE}

library(Hmisc)
fa.6F.1 <- fa(r=correlations$rho, nfactors = 6, fm= "pa",rotate ="varimax",
              residuals = TRUE, SMC = TRUE, n.obs =428)
DD <- print(fa.6F.1, cut = .3, digits = 3, sort = TRUE)

reduced.model.6F.1 <- dplyr::select(EFA.data ,
                                    -c(item32, item34, item44,item24, item37, item22, item5,
                                        item28,item39,item23, item45, item6, item29, item2, item41, item30))

correlations.red.6F.2 <- polychoric(reduced.model.6F.1,correct = 0)

fa.6F.2 <- fa(r=correlations.red.6F.2$rho, nfactors = 6, fm= "pa",rotate ="varimax",
              residuals = TRUE, SMC = TRUE, n.obs =428)

EE <- print(fa.6F.2, cut = .3, digits = 3, sort = TRUE)
reduced.model.6F.2 <- dplyr::select(EFA.data ,
                                    -c(item32, item34, item44,item24, item37, item22, item5,
                                        item28,item39,item23, item45, item6, item29, item2, item41, item30, item46, item36,item1, item25))
correlations.red.6F.3 <- polychoric(reduced.model.6F.2,correct = 0)
fa.6F.3 <- fa(r=correlations.red.6F.3$rho, nfactors = 6, fm= "pa",rotate ="varimax",
              residuals = TRUE, SMC = TRUE, n.obs =428)
FF <- print(fa.6F.3, cut = .3, digits = 3, sort = TRUE)

reduced.model.6F.3 <- dplyr::select(EFA.data ,
                                    -c(item32, item34, item44,item24, item37, item22, item5,
                                        item28,item39,item23, item45, item6, item29, item2, item41, item30, item46, item36,item1, item25, item18))
correlations.red.6F.4 <- polychoric(reduced.model.6F.3,correct = 0)
fa.6F.4 <- fa(r=correlations.red.6F.4$rho, nfactors = 6, fm= "pa",rotate ="varimax",
              residuals = TRUE, SMC = TRUE, n.obs =428)
FF <- print(fa.6F.4, cut = .3, digits = 3, sort = TRUE)

efa.table.2 <- tabledown::fac.tab(fa.6F.4,.3, complexity = F) 
```

```{r EFAsix, results='asis'}
apa_table(efa.table.2, caption = "Factor loadings and communality of the retained items in six factor solution [Unmerged Responses]", note = "Only loading higher than .30 is reported", longtable =T, font_size = "small")
```

## Items Retained in the Five Factor Solution [Unmerged Responses]

| **Five Factor Solution [Unmerged Responses] (24 Items)** |
|---------------------------------------------------------|
| **F1**                                                  |
| `r label(sem.data$item19)`                              |
| `r label(sem.data$item20)`                              |
| `r label(sem.data$item18)`                              |
| `r label(sem.data$item21)`                              |
| `r label(sem.data$item4)`                               |
| **F2**                                                  |
| `r label(sem.data$item11)`                              |
| `r label(sem.data$item10)`                              |
| `r label(sem.data$item12)`                              |
| `r label(sem.data$item8)`                               |
| `r label(sem.data$item7)`                               |
| `r label(sem.data$item9)`                               |
| **F3**                                                  |
| `r label(sem.data$item3)`                               |
| `r label(sem.data$item27)`                              |
| `r label(sem.data$item40)`                              |
| **F4**                                                  |
| `r label(sem.data$item35)`                              |
| `r label(sem.data$item48)`                              |
| `r label(sem.data$item33)`                              |
| `r label(sem.data$item47)`                              |
| `r label(sem.data$item44)`                              |
| `r label(sem.data$item31)`                              |
| `r label(sem.data$item38)`                              |
| **F5**                                                  |
| `r label(sem.data$item16)`                              |
| `r label(sem.data$item17)`                              |
| `r label(sem.data$item36)`                              |

```{r Timetab, include=FALSE, warning=F,message=FALSE}
descriptives.data%>%
  tbl_summary(
    label = slypos_demographics_tz.factor ~ "Time zone - Country",
    statistic = list(all_categorical() ~ "{n} ({p}%)"),
    missing = "no",
    sort = all_categorical() ~ "frequency",
    include = "slypos_demographics_tz.factor"
  )  %>% bold_labels() %>% 
  modify_header(label ~ "") %>%
  modify_caption("Geographical Location") -> tz_table

  as_tibble(tz_table, format = 'pipe') -> tz_tibble

as_kable(tz_table, format = "latex",booktabs = T, longtable =T) -> tz_kable

```

```{r tztabprint, results='asis'}

tz_kable %>% 
  kable_styling(latex_options = c("repeat_header")) %>% 
  column_spec(1,width = "10cm") %>% 
  column_spec(2,width = "2cm")

```

>>>>

```{r factormp, warning=F}
map <- readr::read_csv("Table_raw/map_stat")
map1 <- (map$`MAP Statistic`)

map1 <- MOTE::apa(map1,5,F)
map1 <- as.character(map1)
map1 <- as.data.frame(map1)
colnames(map1) <- "MAP Statistics"
map2 <- map[,-c(1,2)]
map3 <- cbind(map1, map2)

papaja::apa_table(map3, caption = "Map Statistics")
```

```{r MI, include=F, warning=F}
data <- readRDS("leba_2021-09-08.rds")

@@

mi.desc_table <- CFA.descriptives[,c(1,2,5,6,7)] %>%
  tbl_summary(
    by = slypos_demographics_language.factor,
    statistic = list(all_continuous() ~ "{mean} ({sd})",
                     all_categorical() ~ "{n} ({p}%)"),
    digits = all_continuous() ~ 2,
    label = list(slypos_demographics_age ~ "Age",
                 slypos_demographics_sex.factor ~ "Sex",
                 slypos_demographics_work_or_school.factor ~ "Occupational Status",
                 slypos_demographics_school.factor ~ "Occupational setting"
                 ),
    missing = "no"
    ) %>% add_overall() %>% bold_labels() %>% add_p() %>% add_q() %>%
modify_header(label ~ "**Variable**") %>% separate_p_footnotes() %>%
  modify_caption("Demographic Characteristics: Native English Speakers")

mides_kable <-  as_kable_extra(mi.desc_table, format = "latex",booktabs = T) 
```

```{r midesp, warning=F, message=F}
mides_kable %>% 
  kable_styling(latex_options = c("scale_down")) 
```

```{r F1IF, echo=FALSE, fig.align='center', fig.cap='Item information curve of LEBA F1', out.height='160%', out.width='100%'}
knitr::include_graphics('Manuscript.figures/F1.itemplots.png')
```

```{r F2IF, echo=FALSE, fig.align='center', fig.cap='Item information curve of LEBA F1', out.height='160%', out.width='100%'}
knitr::include_graphics('Manuscript.figures/F2.itemplots.png')
```

```{r F3IF, echo=FALSE, fig.align='center', fig.cap='Item information curve of LEBA F1', out.height='160%', out.width='100%'}
knitr::include_graphics('Manuscript.figures/F3.itemplots.png')
```

```{r F4IF, echo=FALSE, fig.align='center', fig.cap='Item information curve of LEBA F1', out.height='160%', out.width='100%'}
knitr::include_graphics('Manuscript.figures/F4.itemplots.png')
```

```{r F5IF, echo=FALSE, fig.align='center', fig.cap='Item information curve of LEBA F1', out.height='160%', out.width='100%'}
knitr::include_graphics('Manuscript.figures/F5.itemplots.png')
```

```{r personfit, fig.cap="Person fit of the five fitted IRT models (a) Wearing blue light filters (b) Spending time outdoors (c) Using phone and smartwatchin bed (d) Using light before bedtime (e) Using light in the morning andduring daytime", warning=FALSE, out.width="100%", out.height="120%"}
knitr::include_graphics("Manuscript.figures/personfit.png")
```
